\begin{Large}
\centertext{Abstract}
\end{Large}

\noindent CAD development project discuss the work done in computer-aided-design. Computer-aided design (CAD) is the use of computer systems to assist in the creation, modification, analysis, or optimization of a design. I explored  LibreCAD  Source  Code. LibreCAD is Free and Open Source CAD Software. LibreCAD is a  fully  comprehensive  2D  CAD   application  that  you  can  download  and  install  for  free.  There  is  a  large base  of  satisfied  LibreCAD   users  worldwide,  and  it  is  available  in  more  than  20  languages  and  for  all
major  operating  systems,  including  Microsoft  Windows,  Mac  OS  X  and  Linux .  Librecad  is  an  application  for  computer  aided  design  in  two dimensions  .  With  librecad   you   can  create  technical  drawings  such  as  plans  for  buildings,  interiors,
mechanical parts or schematics and diagrams. Basically, LibreCAD is used to make 2D design. \\

\noindent This project also includes work regarding qt creater to make a text editor, based upon which we have implemeneted the LibreCAD3 load/save feature for lua scripting. Qt Creator is a cross-platform C++, JavaScript and QML integrated development environment which is part of the SDK for the Qt GUI Application development framework. Using qt we have created the GUI for our new project GDCAD now eCAD.\\

\noindent It also involves the introduction to a constraint solver i.e Minion is a solver for constraint satisfaction problems. Unlike constraint programming toolkits, which expect users to write programs in a traditional programming language like C++, Java or Prolog, Minion takes a text file which specifies the problem, and solves using only this. This makes using Minion much simpler, at the cost of much less customization.\\

\noindent Also, this project is completely open source and the entire code is available 
to the user as and when required. There is also Complete developer's 
Documentation as well as User manual alongwith it that helps using it a lot easier.
