\newpage
\section{Minion - A Constraint Solver}
Minion is a solver for constraint satisfaction problems. Unlike constraint programming toolkits, which expect users to write programs in a traditional programming language like C++, Java or Prolog, Minion takes a text file which specifies the problem, and solves using only this. This makes using Minion much simpler, at the cost of much less customization.\\

\noindent Minion is a new constraint solver, which is very fast and scales well as problem size increases. Empirical results on standard benchmarks show orders of magnitude performance gains over state-of-the-art constraint toolkits. These gains increase with problem size --- MINION delivers scalable constraint solving.\\

\noindent Minion is a general-purpose constraint solver, with an expressive input language based on the common constraint modelling device of matrix models. Focussing on matrix models supports a lean, highly-optimised implementation. This contrasts with current constraint toolkits, which, in order to provide ever more modelling and solving options, have become progressively more complex at the cost of both performance and usability.\\

\noindent Minion is a black box from the user point of view, deliberately providing few options. This, combined with its raw speed, makes MINION a substantial step towards Puget's `Model and Run' constraint solving paradigm. \\

\noindent Minion is Open Source software, licensed under GNU General Public License Version 2. Minion is maintained as a SourceForge project. There is a MINION mailing list, details of which can be found at: https://mailman.cs.st-andrews.ac.uk/mailman/listinfo/mug\\
