\section{Introduction}
The  term  computer  graphics  includes  almost  everything  on  computers  that  is  not  text  or  sound.  Today
almost  every  computer  can  do  some  graphics,  and  people  have  even  come  to  expect  to  control  their
computer  through  icons  and  pictures  rather  than  just  by  typing.  Here  in  our  lab  at  the  Program  of
Computer  Graphics,  we  think  of  computer  graphics  as  drawing  pictures  on  computers,  also  called
rendering.  The  pictures  can  be photographs, drawings, movies, or simulations ­­ pictures of things which
do  not  yet  exist  and  maybe  could   never  exist.  Or  they  may  be  pictures  from  places  we  cannot  see
directly,  such  as  medical  images  from  inside  your  body.  Computer  graphics  is  now  used  in  various
fields;  for  industrial,  educational,  medical  and  entertainment  purposes.  The  aim  of  computer  graphics  is
to  visualize  real  objects  and  imaginary  or  other  abstract  items.  In  order to visualize various things, many
technologies  are  necessary  and  they  are  mainly  divided  into  two  types  in  computer  graphics:  modeling
and  rendering  technologies.\\

\section{Introduction to CAD}
Computer-aided design (CAD) is the use of computer systems to assist in the creation, modification, analysis, or optimization of a design. CAD software is used to increase the productivity of the designer, improve the quality of design, improve communications through documentation, and to create a database for manufacturing.CAD is an important industrial art extensively used in many applications, including automotive, shipbuilding, and aerospace industries, industrial and architectural design, prosthetics, and many more. CAD is also widely used to produce computer animation for special effects in movies, advertising and technical manuals. CAD output is often in the form of electronic files for print, machining, or other manufacturing operations. CAD is also used for the accurate creation of photo simulations that are often required in the preparation of Environmental Impact Reports, in which computer-aided designs of intended buildings are superimposed into photographs of existing environments to represent what that locale will be like were the proposed facilities allowed to be built.  Computer­ Aided  Drafting  describes  the  process  of  creating  a
technical  drawings with the use of computer software. CAD software is used to increase the productivity
of  the  designer,  improve  the  quality  of  design,  improve  communications  through  documentation,  and  to
create  a  database  for  manufacturing.  CAD  output  is  often  in  the  form  of  electronic  files  for  print  or
machining  operations.  CAD  software  uses  either  vector  based  graphics  to  depict  the  objects  of
traditional  drafting,  or  may  also  produce  raster  graphics  showing  the  overall   appearance  of  designed
objects.\\


Today  there  are  very  few  aspects  of  our  lives  not  affected  by  computers.  Practically  every  cash or
monetary  transaction  that  takes  place  daily  involves  a  computer.  In  many  cases,  the  same  is  true  of
computer  graphics.  Whether  you  see  them  on  television,  in  newspapers,  in  weather   reports  or  while  at
the  doctor’s  surgery,  computer  images  are  all  around  you.  “A  picture  is  worth  a  thousand  words”  is  a
well ­known  saying  and  highlights  the  advantages  and  benefits  of  the  visual ation of our data. We
are  able  to  obtain  a  comprehensive  overall  view  of  our  data  and   also  study  features  and  areas  of
particular  interest. A  range  of  tools
and  facilities  are  available  to  enable  users  to  visualize  their  data,  and  this  document  provides  a  brief
summary  and  overview.  Computer  graphics  can  be  used  in  many  disciplines.  Charting,  ations,
Drawing,  Painting  and  Design,  Image  Processing  and  Scientific  Visualization  are  some  among  them.
Computer  graphics  is concerned with all aspects of producing images using a computer. It concerns with
the pictorial synthesis of real or imaginary objects from their computer­based models.\\


CAD  often  involves  more  than  just  shapes.  As  in  the  manual  drafting  of  Technical  and  Engineering
Drawings,  the  output  of  CAD  must  convey  information,  such  as  material,  processes,dimensions  and
tolerances,  according  to  application­specific  conventions.  CAD  may  be  used  to  design  curves  and
figures  in  two­Dimensional(2D)  space;  or  curves,  surfaces,  and  solids  in  three  dimensional(3D)
space.CAD  is  an  important  industrial  art  extensively  used  in  many  applications,  including  automotive,
shipbuilding,  and  aerospace  industries,  industrial  and  architectural  design, prosthetic,  and  many  more.
CAD  is  also  widely  used  to  produce  Computer  animation  for  special  Effects  in  movies,advertising  and
technical  manuals.  The  modern  ubiquity  and  power  of  computers  means  that  even  perfume  bottles  and
shampoo  dispensers  are  designed  using   techniques unheard of by engineers of the 1960s. Because  of its
enormous  economic  importance,  CAD  has  been  a  major  driving  force  for  research  in  computational
geometry,  computer  graphics  (both  hardware  and  software),  and  discrete  differential  geometry.The
design  of  geometric  model  for  object  shapes,  in  particular,  is  occasionally  called  Computer ­Aided
Geometric  Design  (CAGD).While  the  goal  of  automated  CAD  systems  is to increase efficiency, they are
not  necessarily  the  best  way   to  allow  newcomers  to  understand  the  geometrical  principles  of  Solid
Modeling.\\


I  explore  LibreCad  Source  Code.  LibreCAD is Free and Open Source CAD Software.LibreCAD is
a  fully  comprehensive  2D  CAD   application  that  you  can  download  and  install  for  free.  There  is  a  large
base  of  satisfied  LibreCAD   users  worldwide,  and  it  is  available  in  more  than  20  languages  and  for  all
major  operating  systems,  including  Microsoft  Windows,  Mac  OS  X  and  Linux  (Debian,  Ubuntu,
Fedora,  Mandriva,  Suse  ...).  Librecad  is  an  application  for  computer  aided  design  (cad)  in  two
dimensions  (2d).  with  librecad   you   can  create  technical  drawings  such  as  plans  for  buildings,  interiors,
mechanical parts or schematics and diagrams.\\


The  app  is  great  for  industrial  designers,  but  anyone  who  wants  to  learn  how  to  make  2D  CAD
drawings  will  like  this  program.  For  a  free  software,  LibreCAD  gives  you  a  lot  of  tools  to  work  with.
New  users  will  be  able  to  create  basic drawings, while advanced users can make engineering plans with
5the  software.  Layers  can  be  added,  ideal  for  complex   drawings.  The  provided  tools  are  sufficient  for
producing  high  precision  drawings.  You  can  start  drawings  from  scratch.  But  it  is  also  easy  to  put  in
splines,  ellipses,  arcs,  lines  and   circles.  A  single  item  can  have  several iterations. For instance, you have
4 modes for a rectangle parameter. The different shapes can be combined easily.
LibreCAD  also  has  a  powerful  zoom  tool  that  lets  you  look  at  models  at  different  distances.  This  is
essential  for  designers  who  are  going  to  make  life­size  copies  of  a  drawing.  There are three tabs above
the  working  area.   The  first  tab  is  for  changing  color,  useful  for  layer  definition.   The  other  tab  is  for
changing size and the third for workspace customization.\\


LibreCAD also has grids which are extremely useful for those new to CAD. Once you have  made the
basic  object,  you can customize it in many ways. Scaling is particularly easy here. Also worth mentioning
here  is  the  "Explode  text  into  letters"  effect.   It  is  a  special  feature  that  will come in handy ations.
LibreCAD  allows  you  to  put  horizontal  or vertical restrictions on completed models. Relative zeros may
be  locked,  useful  for   ending  and  starting  points.  All  in  all,  it is powerful, free CAD application. You can
download, install and distribute LibreCAD freely, with no fear of copyright infringement.
